### 2016-10-12 methodsPaper/tex/introduction.tex
Tested pucher2010 reference in methods paper
Seems like it worked.

To better understand the potential for attainable shifts in
transportation behavior across the US, we employed a comparative risk
assessment methodology to compare national averages for time spent
walking and cycling for transport to those of specific states. Our
estimates can provide an important evidence base to encourage new
construction, retrofits, land use policy, and programatic funding to
support active transportation. Particularly in places with poor
attainmnet of the physical activity guidelines, such investments can
be important pieces of larger population health interventions that
have effective and long-lasting impacts.

ITHIM is a statistical model that integrates data on travel patterns,
physical activity, fine particulate matter, GHG emissions, and disease
and injuries. Based on population and travel scenarios. The model has
been used to calculate the health impacts of walking and bicycling
short distances usually traveled by car or driving low-emission
automobiles \cite{woodcock2013,maizlish2013}.

The ITHIM model uses comparative risk assessment through which it
formulates a change in the disease burden, resulting from the shift in
the exposure distribution from a baseline scenario to an alternative
scenario.

>>>>

%% To better understand the potential for attainable shifts in
%% transportation behavior across the US, we employed a comparative risk
%% assessment methodology to compare national averages for time spent
%% walking and cycling for transport to those of specific states. Our
%% estimates can provide an important evidence base to encourage new
%% construction, retrofits, land use policy, and programatic funding to
%% support active transportation. Particularly in places with poor
%% attainmnet of the physical activity guidelines, such investments can
%% be importnat pieces of lareger population health interventions that
%% have effective and long-lasting impacts.

ITHIM is a statistical model that integrates data on active transport,
physical activity, fine particulate matter and greenhouse gas
emissions to provide estimates for the proportional change in
mortality and morbidity for given baseline and alternate travel
scenarios. The model has been used to calculate the health impacts of
walking and bicycling short distances usually traveled by car or
driving low-emission automobiles \cite{woodcock2013,maizlish2013}.

ITHIM uses a comparative risk assessment framework for the active
transport component of the model.  We improve on the existing
implementation of the active transport component by including the
distribution of non-travel-related activity, improving numerical
precision when computing the population attributable fraction and
creating a simple user-interface for the custom-built \R{}
package \package{}.

Dummy ref \cite{pucher2010}.
